\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-04-24 paper/main.tex
Updated spacing, fixed some text

\textbf{Bugs.}~We focus on issue reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the issue reports have the label "bug" and have been fixed with pull
requests linked to them. We then create a filter that incorporates
the periods mentioned above, the label, the issue status being closed
and the presence of a linked pull request. We found \numtorchfiltered{}
issues for \torch, \numtffiltered{} issues for \tf, and \numjaxfiltered{}
issues for \jax after filtering the issues. \torch has the highest number
of issues due to a lack of a label for bugs in the issue tracker.
%%
Then, we manually inspect the filtered issues to ensure that they
contain enough information to reproduce the bug, i.e., code to
reproduce the bug, dependencies required for the bug reproduction,
clear description of the desired behavior, etc. We discard bugs that
are not in the core functionality of the library e.g. documentation
issues, feature requests, etc. After this stage of manual inspection,
we end up with \numtorchinspected{} issues for \torch,
\numtfinspected{} issues for \tf, and \numjaxinspected{} issues for
\jax.
%
Finally, we do a deeper analysis on these bugs. We find some bugs that
are related to building/installation/problematic unit tests instead of
bugs in the core API functionality, as well as some bugs that lack any
code snippet provided with the bug report to reproduce the bug. These
bugs can be detected and discarded at this stage.
We assess the reproducibility of a bug by creating a
virtual environment that contains the necessary dependencies to
reproduce the bug. Some bugs require very specific hardware (e.g. TPU) 
or can not be reproduced due to an expired nightly build that can no
longer be accessed. We successfully reproduce the bug if none of these
issues are present by
creating the enviroment detailed in the report, and we include the
corresponding artifacts in our dataset. Throughout this process, we
obtain \textbf{\numjaxbugs{}}, \textbf{\numtorchbugs{}}, and
\textbf{\numtfbugs{}} bug instances for \jax, \torch, and \tf,
respectively.

@@

\subsection{Challenges}
\label{sec:challenges}

@@

\subsection{Method}
\label{sec:method}

The following steps show the method we use to create bug instances:

\begin{enumerate}[leftmargin=0.5cm]
  \item Select an issue following the criteria defined in Section~\ref{sec:selection-criterion};
  \item Identify the version of the library used to report the bug along with other dependencies;
  \item Write a \CodeIn{requirements.txt} file with the list of dependencies to reproduce the bug;
  \item Create a file showing the code that causes the bug (for documentation);
  \item Create a file with a \CodeIn{pytest} test case that passes if
    the code triggers the buggy behavior documented in the issue;
    %% A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
  \item If the bug depends on a CUDA-specific build, write a
    Dockerfile to create a container including the needed CUDA-driver
    and the other artifacts mentioned above (e.g., test file and
    requirements);
    %% along with the requirements.txt file and the python
    %% script copied into it.
  \item Write a script that creates the virtual environment (either
    Python's \CodeIn{Conda Enviroment}~\cite{venv} or Docker container) and runs
    the test on it;
  \item Create a directory \CodeIn{<lib>/<bug-id>} containing all the
    artifacts mentioned above, where \CodeIn{lib} refers to the
    affected library and \CodeIn{bug-id} is a fresh identifier of the
    bug instance.
    %% All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
\end{enumerate}

\textbf{Test Oracles.}~
The bug reproduction code includes python tests (pytest). The test
oracle is satisfied when the bug is reproduced successfully. For bugs
that throw an unexpected exception, the test catches the exception and
reports the exception details along with a pass status. For bugs that
result in incorrect output value, assertions are placed in the code to
expect the incorrect output value, hence passing the test when the bug
occurs. For bugs that crash after raising a signal, the code snippet
is placed in a seperate file and executed, while the file contaning
the actual test asserts the presence of the signal raised by the
code. Upon successful reproduction, the original code crashes raising
the proper signal and the assertion passes.
% \Fix{Please review and revise}

\textbf{Example}
% ~\Fix{Can you show here the artifacts associated to bug
%   120903 that you will use in the next section? If it takes too much
%   space, show only directory with files and the test case. - Abid: by the test case, do you mean the python code used to reproduce the bug?} 
  The issue no. 120903 in \torch\ has the following test code that checks the oracle:

\begin{lstlisting}[language=python,basicstyle=\small,]
def test_f():
  input_data = torch.randn(3, 4, 5, 6)
  scale = np.array([0.1, 0.2, 0.3, 0.4])
  zero_point = torch.tensor([1, 2, 3, 4], dtype=torch.int32)
  axis = 1
  quant_min = 0
  quant_max = 255
  with pytest.raises(RuntimeError) as e_info:
      output = torch.fake_quantize_per_channel_affine(input_data, torch.from_numpy(scale), zero_point, axis, quant_min, quant_max)
  print(f'{e_info.type.__name__}: {e_info.value}')
\end{lstlisting}

In this example, the unexpected behavior is a \CodeIn{RuntimeError} thrown by the call to the \CodeIn{fake\_quantize\_per\_channel\_affine} API from \torch. Since the test oracle should pass when the bug is successfully reproduced, the code catches the exception and prints information about it, and upon catching the exception successfully, the test passes. If the bug reproduction fails i.e. the exception is not thrown or a different exception is thrown, the test will fail.

\section{\tname} % : Database of Bugs in DL libraries

@@

\subsection{Contributions}

@@

\section{Related Work}

@@

% Defects4J\cite{just2014defects4j}
% BugsInPy~\cite{widyasari2020bugsinpy} Tests4Py~\cite{smytzek2024tests4py}
% Denchmark~\cite{kim2021denchmark}

\section{Conclusion and Future Work}
Deep Learning Libraries provide the basic blocks for creating
AI-enabled applications. Several testing techniques have been proposed
in the literature to find bugs in these libraries. Unfortunately, the
lack of a dataset of reproducible bugs in those libraries poses an
important barrier to the proper evaluation of these
techniques. \tname{} fills this gap. It includes a total of
\numbugs\ bugs across three major DL libraries and provides an
infrastructure to evaluate fuzzers.  To facilitate evaluation of
testing techniques even further we plan to continue expanding this
dataset and to explore automated approaches to ``frontport'' bugs into
single version of the library as in the Magma
benchmark~\cite{hazimeh2020magma}.

>>>>

\textbf{Bugs.}~We focus on issue reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the issue reports have the label "bug" and have been fixed with pull
requests linked to them. We then create a filter that incorporates
the periods mentioned above, the label (bug), the issue status being closed
and the presence of a linked pull request. We found \numtorchfiltered{}
issues for \torch, \numtffiltered{} issues for \tf, and \numjaxfiltered{}
issues for \jax after filtering the issues. \torch has the highest number
of issues due to a lack of a label for bugs in the issue tracker.
%%
Then, we manually inspect the filtered issues to ensure that they
contain enough information to reproduce the bug, i.e., code to
reproduce the bug, dependencies required for the bug reproduction,
clear description of the desired behavior, etc. We discard cases that
are not in the core functionality of the library e.g. documentation
issues, feature requests, etc. After this stage of manual inspection,
we end up with \numtorchinspected{} issues for \torch,
\numtfinspected{} issues for \tf, and \numjaxinspected{} issues for
\jax.
%
Finally, we do a deeper analysis on these bugs. We find some cases that
are related to building/installation/problematic unit tests instead of
bugs in the core API functionality, as well as some bugs that lack any
code snippet provided with the bug report to reproduce the bug. These
bugs can be detected and discarded at this stage.
We assess the reproducibility of a bug by creating a
virtual environment that contains the necessary dependencies to
reproduce the bug. Some bugs require very specific hardware (e.g. TPU) 
or can not be reproduced due to an expired nightly build that can no
longer be accessed. We successfully reproduce the bug if none of these
issues are present by
creating the enviroment detailed in the report, and we include the
corresponding artifacts in our dataset. We use a virtual enviroment
(conda~\cite{venv}) when the bug can be reproduced on a CPU, and we use docker
containers~\cite{merkel2014docker} with appropriate CUDA drivers when the bug 
requires a GPU.
Throughout this process, we
obtain \textbf{\numjaxbugs{}}, \textbf{\numtorchbugs{}}, and
\textbf{\numtfbugs{}} bug instances for \jax, \torch, and \tf,
respectively.

@@

\vspace{-1ex}
\subsection{Challenges}
\label{sec:challenges}

@@

\subsection{Method}
\label{sec:method}
The following steps show the method we use to create bug instances:
\vspace{-5mm}
\begin{enumerate}[leftmargin=0.5cm]
  \item Select an issue following the criteria defined in Section~\ref{sec:selection-criterion};
  \item Identify the version of the library used to report the bug along with other dependencies;
  \item Write a \CodeIn{requirements.txt} file with the list of dependencies to reproduce the bug;
  \item Create a file showing the code that causes the bug (for documentation);
  \item Create a file with a \CodeIn{pytest} test case that passes if
    the code triggers the buggy behavior documented in the issue;
    %% A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
  \item If the bug depends on a CUDA-specific build, write a
    Dockerfile to create a container including the needed CUDA-driver
    and the other artifacts mentioned above (e.g., test file and
    requirements);
    %% along with the requirements.txt file and the python
    %% script copied into it.
  \item Write a script that creates the virtual environment (either
    Python's \CodeIn{Conda Enviroment}~\cite{venv} or Docker container) and runs
    the test on it;
  \item Create a directory \CodeIn{<lib>/<bug-id>} containing all the
    artifacts mentioned above, where \CodeIn{lib} refers to the
    affected library and \CodeIn{bug-id} is a fresh identifier of the
    bug instance.
    %% All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
\end{enumerate}
\textbf{Test Oracles.}~
The bug reproduction code includes python tests (pytest). The test
oracle is satisfied when the bug is reproduced successfully. For bugs
that throw an unexpected exception, the test catches the exception and
reports the exception details along with a pass status. For bugs that
result in incorrect output value, assertions are placed in the code to
expect the incorrect output value, hence passing the test when the bug
occurs. For bugs that crash after raising a signal, the code snippet
is placed in a seperate file and executed, while the file contaning
the actual test asserts the presence of the signal raised by the
code. Upon successful reproduction, the original code crashes raising
the proper signal and the assertion passes.
% \Fix{Please review and revise}

\textbf{Example}
% ~\Fix{Can you show here the artifacts associated to bug
%   120903 that you will use in the next section? If it takes too much
%   space, show only directory with files and the test case. - Abid: by the test case, do you mean the python code used to reproduce the bug?} 
  The issue no. 120903 in \torch\ has the following test code that checks the oracle:
\vspace{-1ex}
\begin{lstlisting}[language=python,basicstyle=\small,]
def test_f():
  input_data = torch.randn(3, 4, 5, 6)
  scale = np.array([0.1, 0.2, 0.3, 0.4])
  zero_point = torch.tensor([1, 2, 3, 4], dtype=torch.int32)
  axis = 1
  quant_min = 0
  quant_max = 255
  with pytest.raises(RuntimeError) as e_info:
      output = torch.fake_quantize_per_channel_affine(input_data, torch.from_numpy(scale), zero_point, axis, quant_min, quant_max)
  print(f'{e_info.type.__name__}: {e_info.value}')
\end{lstlisting}
\vspace{-1ex}
In this example, the unexpected behavior is a \CodeIn{RuntimeError} thrown by the call to the \CodeIn{fake\_quantize\_per\_channel\_affine} API from \torch. Since the test oracle should pass when the bug is successfully reproduced, the code catches the exception and prints information about it, and upon catching the exception successfully, the test passes. If the bug reproduction fails i.e. the exception is not thrown or a different exception is thrown, the test will fail.

\vspace{-1ex}
\section{\tname} % : Database of Bugs in DL libraries

@@

\vspace{-1ex}
\subsection{Contributions}

@@

\vspace{-1ex}
\section{Related Work}

@@

% Defects4J\cite{just2014defects4j}
% BugsInPy~\cite{widyasari2020bugsinpy} Tests4Py~\cite{smytzek2024tests4py}
% Denchmark~\cite{kim2021denchmark}
\vspace{-1ex}
\section{Conclusion and Future Work}
Deep Learning Libraries provide the basic blocks for creating
AI-enabled applications. Several testing techniques have been proposed
in the literature to find bugs in these libraries. Unfortunately, the
lack of a dataset of reproducible bugs in those libraries poses an
important barrier to the proper evaluation of these
techniques. \tname{} fills this gap. It includes a total of
\numbugs\ bugs across three major DL libraries and provides an
infrastructure to evaluate fuzzers.  To facilitate evaluation of
testing techniques even further we plan to continue expanding this
dataset and to explore automated approaches to ``frontport'' bugs into
single version of the library as in the Magma
benchmark~\cite{hazimeh2020magma}.
